Coordinated shifts in allocation among reproductive tissues across 14 coexisting plant species

### 2017-05-22 ms/Accessory/Wenk-Accessory-SI.Rnw
Better readme, links, Clean analysis script

Code reproducing the results described in this paper is available at \\ \href{https://github.com/traitecoevo/reproductive_allocation_kuringai}{github.com/traitecoevo/reproductive\_allocation\_kuringai}. Further instructions on running the code are available at that address. Here we simply provide a brief overview of the content. The folder \texttt{R} contains functions implementing the methods described above and in the main text as follows.

>>>>

Code reproducing the results described in this paper is available at \\ \href{https://github.com/traitecoevo/reproductive_allocation_kuringgai}{github.com/traitecoevo/reproductive\_allocation\_kuringgai}. Further instructions on running the code are available at that address. Here we simply provide a brief overview of the content. The folder \texttt{R} contains functions implementing the methods described above and in the main text as follows.
